Turbulence in compact to giant H~II regions

### 2023-04-21 strucfunc_paper.tex
Javier changes 2023-04-21

An alternative approach to determine the velocity variance and correlation length
is to empirically measure \(\sigma\pos^2\) from the observations and then to use linear
interpolation on the measured structure function to find the point where \(B(r_0) = \sigma\pos^2\).
This yields \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.05}{pc} \),
as compared to the model-derived values of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \).
The main reason for the discrepancy is the finite box effect
discussed in section~\ref{sec:finite-box-effects} above, where it is shown
that for homogeneous fluctuations it is necessary to sample a map of size \(L > 10 r_0\)
in order to empirically determine \(\sigma\pos^2\).
In the case of the Orion core observations, \(L = 7 r_0\),
so the fluctuations are not fully sampled, leading
to the empirical \(\sigma\pos^2\) being an underestimate.
However, given the evidence for a radial gradient in the amplitude of the velocity fluctuations,
it could be argued that the finite box effect is not so important as it would be for homogeneous fluctuations
and it is instead the model-derived value of \(\sigma\pos^2\) that is an overestimate.

>>>>

An alternative approach to determine the velocity variance and correlation length
is to empirically measure \(\sigma\pos^2\) from the observations and then to use linear
interpolation on the measured structure function to find the point where \(B(r_0) = \sigma\pos^2\).
This yields \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.05}{pc} \),
as compared to the model-derived values of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
The main reason for the discrepancy is the finite box effect
discussed in section~\ref{sec:finite-box-effects} above, where it is shown
that for homogeneous fluctuations it is necessary to sample a map of size \(L > 10 r_0\)
in order to empirically determine \(\sigma\pos^2\).
In the case of the Orion core observations, \(L = 7 r_0\),
so the fluctuations are not fully sampled, leading
to the empirical \(\sigma\pos^2\) being an underestimate.
However, given the evidence for a radial gradient in the amplitude of the velocity fluctuations,
it could be argued that the finite box effect is not so important as it would be for homogeneous fluctuations
and it is instead the model-derived value of \(\sigma\pos^2\) that is an overestimate.
